Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
sfd
Dust

% typography
\setlength{\parindent}{1.\baselineskip}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\pans}{\textsl{Pan-STARRS}}
\newcommand{\DR}{\acronym{DR2}}
\newcommand{\msun}{\textrm{M}_\odot}
\newcommand{\kpc}{\textrm{kpc}}
\newcommand{\kms}{\ensuremath{\textrm{km}~\textrm{s}^{-1}}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\masyr}{\ensuremath{\textrm{mas}~\textrm{yr}^{-1}}}
\newcommand{\feh}{\ensuremath{[\textrm{Fe} / \textrm{H}]}}
\newcommand{\article}{\textsl{Letter}}

@@

\subselection{Stream member selection}

@@

\figurename~\ref{fig:selection} (bottom left) shows the final sample of GD-1
stream member candidates after selecting on both proper motions and photometry.
\todo{Comment on how this is the bomb ass diggity and the clearest view of the
stream so far}

\subselection{Stream member selection}

Comment on these here - add figure for both in Appendix?
- Dust / no significant extinction - combine with other figure
- Scanning pattern - just discuss, no figure

Most of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 35^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd} shows the $V$-band extinction in the region around the
GD-1 stream, computed from the Schlegel-Finkbeiner-Davis extinction map
(\cite{Schlegel:1998}; hereafter SFD).
Vertical lines indicate the two regions clearly identifiable as under-densities
from the proper-motion-selected stream members.
The maximum $A_V$ is $\approx$0.07 mag in both the under-density and gap
regions.
The dispersion in $A_V$ in the region $-60^\circ < \phi_1 < 0^\circ$ and
$-1^\circ < \phi_1 < 1^\circ$ is $\sigma_{A_V} \approx 0.03~\textrm{mag}$.

% Notebook: GD1-dust-and-completeness
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{sfd.pdf}
\end{center}
\caption{%
Colored background shows the $V$-band extinction, $A_V$, in the GD-1
coordinate system.
Vertical lines roughly show the extents the identified under-density (UD) and
gap.
The maximum extinction in the UD or Gap regions is $\approx$0.07 mag.
\label{fig:sfd}
}
\end{figure}

@@

\appendix
\section{Completeness check and data validation}
\label{sec:validate}

>>>>

% typography
\setlength{\parindent}{1.\baselineskip}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\pans}{\textsl{Pan-STARRS}}
\newcommand{\DR}{\acronym{DR2}}
\newcommand{\msun}{\textrm{M}_\odot}
\newcommand{\kpc}{\textrm{kpc}}
\newcommand{\mag}{\textrm{mag}}
\newcommand{\kms}{\ensuremath{\textrm{km}~\textrm{s}^{-1}}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\masyr}{\ensuremath{\textrm{mas}~\textrm{yr}^{-1}}}
\newcommand{\feh}{\ensuremath{[\textrm{Fe} / \textrm{H}]}}
\newcommand{\article}{\textsl{Letter}}

@@

@@

\figurename~\ref{fig:selection} (bottom left) shows the final sample of GD-1
stream member candidates after selecting on both proper motions and photometry.
\todo{Comment on how this is the bomb ass diggity and the clearest view of the
stream so far}
\todo{Mention the under-densities}
\todo{Already mention the spur here}

All of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 20^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd} shows the $V$-band extinction in the region around the
GD-1 stream, computed from the Schlegel-Finkbeiner-Davis extinction map
(\cite{Schlegel:1998}; hereafter SFD).
For stream longitudes $-60^\circ < \phi_1 < 10^\circ$ and $-1^\circ < \phi_2 <
1^\circ$, the median $V$-band extinction is $\textrm{med}\left(A_V\right) =
0.04~\mag$, and the dispersion in $A_V$ in this region is $\sigma_{A_V} \approx
0.03~\textrm{mag}$.
For longitudes $\phi_1 < -60^\circ$, as the stream approaches the Galactic disk,
dust extinction becomes more appreciable.

Another \todo{segue to this paragraph...}.
However, we find that \todo{...}.
We discuss the scanning pattern in more detail in
Appendix~\ref{sec:completeness}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{sfd.pdf}
\end{center}
\caption{%
Colored background shows the $V$-band extinction, $A_V$, in the GD-1
coordinate system.
Vertical lines roughly show the extents the identified under-density (UD) and
gap.
The maximum extinction in the UD or Gap regions is $\approx$0.07 mag.
\label{fig:sfd}
}
\end{figure}

@@

\appendix
\section{Completeness check and scanning pattern}
\label{sec:completeness}
